%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Deedy - One Page Two Column Resume
% LaTeX Template
% Version 1.2 (16/9/2014)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Deedy - One Page Two Column Resume
% LaTeX Template
% Version 1.2 (16/9/2014)

% IMPORTANT: THIS TEMPLATE NEEDS TO BE COMPILED WITH XeLaTeX
%
% This template uses several fonts not included with Windows/Linux by
% default. If you get compilation errors saying a font is missing, find the line
% on which the font is used and either change it to a font included with your
% operating system or comment the line out to use the default font.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% 
% TODO:
% 1. Integrate biber/bibtex for article citation under publications.
% 2. Figure out a smoother way for the document to flow onto the next page.
% 3. Add styling information for a "Projects/Hacks" section.
% 4. Add location/address information
% 5. Merge OpenFont and MacFonts as a single sty with options.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% CHANGELOG:
% v1.1:
% 1. Fixed several compilation bugs with \renewcommand
% 2. Got Open-source fonts (Windows/Linux support)
% 3. Added Last Updated
% 4. Move Title styling into .sty
% 5. Commented .sty file.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Known Issues:
% 1. Overflows onto second page if any column's contents are more than the
% vertical limit
% 2. Hacky space on the first bullet point on the second column.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[]{deedy-resume-openfont}
\documentclass[10pt]{report}
\usepackage{fancyhdr}
\usepackage{xcolor}
\fontspec{[fontawesome-webfont.ttf]}
\usepackage{fontawesome}
\pagestyle{fancy}
\fancyhf{}
 
\begin{document}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\namesection{}{Palkit Lohia}{
Research Intern at Indian School of Business, Sophomore @ Economics, IIT Kharagpur}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.33\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education} 

\subsection{IIT Kharagpur}
\descript{Integrated B.Sc + M.Sc IN ECONOMICS \\ CGPA: 9.06/10}
\location{2019-2024| West Bengal, India}
\sectionsep
\\~\\~\\
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     LINKS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{INTEREST AREAS}
\textbf{As an economics student with interest \\in Artificial Intelligence, I have taken courses across Machine Learning and NLP. I am Interested in handling computationally heavy datasets to\\ derive insights for impactful decision making.}
\sectionsep
\\~\\~\\

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     COURSEWORK
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Coursework}
\emph{T - Theory | L - Laboratory}\\
\descript{Completed}
Programming \& Data Structures (T/L)\\
Micro Economics 1 (T)\\
Macro Economics 1 (T)\\
Statistics for Economics (T/L)\\
\descript{Ongoing}
Probability and Statistics (T)\\
\sectionsep
\descript{MOOCs}\\
\href{https://coursera.org/share/9a2868c911ab931492ad1bfc84b3ac75}{Natural Language Processing with Classification and Vector Spaces}\\
\href{https://coursera.org/share/b77c1d962643f8fa066ca076c3f3be10}{Natural Language Processing with Probabilistic Models}\\
\href{https://coursera.org/share/85611fef8e8312607c95a49a5a63fc87}{Discrete Math and Analyzing Social Graphs}\\
\href{https://coursera.org/share/b76987bf1b6c78e3745c91ced9492502}{Linear Algebra for Machine Learning}
\href{https://coursera.org/share/7446c90cce3eeb7deb317fd868c0fa4f}{Introduction to portfolio\\ construction and analysis with python}\\


\\~\\~\\
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     CONTACT
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{CONTACT \& LINKS} 
\faPhone{+91-76799 52548}\\
\faEnvelope\ {\href{mailto:palkitlohia15@iitkgp.ac.in}{ palkitlohia15@iitkgp.ac.in}}\\
\faGithub\ {\href{https://github.com/spookbite}{ spookbite}}\\
\faGlobe\ {\href{https://spookbite.github.io/}{ spookbite.github.io}}\\
\faLinkedinSquare\ {\href{https://www.linkedin.com/in/palkit-l-49aa66195/}{ Palkit Lohia}}\\
\faMap{ LBS Hall,  IIT Kharagpur - 721302 }\\
\sectionsep
 \\~\\
 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage} 
\hfill
\begin{minipage}[t]{0.66\textwidth} 


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     INTERNSHIPS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{INTERNSHIPS}

\runsubsection{RESEARCH INTERNSHIP @ SRITNE, ISB HYDERABAD}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\location{\\REAL TIME INDICES OF ECONOMIC ACTIVITY}

\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item Calculated weekly normal percentage returns of stock prices for Nifty-500 companies and mapped them to their industries.
\item Calculated weekly sentiment scores of tweets by Nifty-500 companies and tweets related to Nifty-500 companies, posted by verified twitter handles.
\item Created a panel-data corresponding to the above results and derived meaningful insights from it. 
\end{tightemize}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\location{\\GENDER ASSIGNMENT OF PATENTS}
\begin{tightemize}
\item Collected data from USPTO website using MINIDOM. Extracted title, abstract and summary of the patents from the XML files containing Patent data.
\item Calculated the TF-IDF score for text corresponding to each patent and classified them as Male or Female.
\end{tightemize}
\vspace{\topsep} % Hacky fix for awkward extra vertical space

\runsubsection{NATURAL LANGUAGE PROCESSING INTERNSHIP @ \href{https://topcrop.in/}{TopCrop.in}}
\begin{tightemize}
\item Assisted with data collection, cleansing, ingestion and wrangling. 
\item Created a cosine-similarity model and calculated TF-IDF scores of product description and classified them into HS Codes.
\end{tightemize}

\\~\\

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%   PROJECTS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{\href{https://github.com/SPOOKBITE/NLP_PROJECTS}{PROJECTS}}
\runsubsection{\href{https://github.com/SPOOKBITE/NLP_PROJECTS}{}}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item \textbf{POS tagging}: Implemented a system to assign a part-of-speech tag (Noun, Verb, Adjective,etc.), using \textbf{Markov chains and Virtebri algorithm}, to each word in an input text.
\item \textbf{Auto Correct}: Implemented an Auto-correct system using \textbf{Levenshtein distance and word probabilities}
\item \textbf{Auto Complete}: Implemented an Auto-complete system using the \textbf{N-gram Language Model} and \textbf{perplexity} to calculate the score.

\end{tightemize}
\vspace{\topsep} % Hacky fix for awkward extra vertical space

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%   SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Technical Skills}
\begin{tabular}{r|p{15cm}}
\textsc{Programming Languages} & \textbf{ C | C++ | Python } \\
\textsc{Databases} & \textbf{ MySQL }\\
\textsc{Python Libraries} & \textbf{Pandas, Numpy, Matplotlib, Scikit-learn, NLTK,\newline Scipy, PyCaret, Joblib, Twint, Vader, LazyPredict}\\ 
\end{tabular}

\\~\\

%----------------------------------------------------------------------------------------
%	Scholastic Achievements
%----------------------------------------------------------------------------------------

\section{SCHOLASTIC ACHIEVEMENTS}

\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}

\item\textbf{{JEE Advanced \emph{AIR 5492}:}} Among the top 0.48\% of the 1.2 million applicants in JEE Mains 2019.
\item\textbf{{JEE Mains \emph{AIR 3230}:}} Among the top 0.28\% of the 1.2 million applicants in JEE Mains 2019. 
\item Recipient of the \textbf{Merit-Cum-Means scholarship} offered by IIT Kharagpur to meritorius students pursuing university education.
\end{tightemize}


%	Activities and Leadership
%----------------------------------------------------------------------------------------

\section{Activities \& Leadership}

\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}


\item \textbf{{\emph{Core Team Member, Kharagpur Open Source Society}:}} Responsible for the smooth conduct of events to familiarize students with open source technologies and philosophy.
\vspace{\topsep} % Hacky fix for awkward extra vertical space

\vspace{\topsep} % Hacky fix for awkward extra vertical space

\end{tightemize}
\sectionsep

\end{minipage} 
\end{document}

